---
title: "Homework 6"
author: "Lauren Ashlock"
date: "February 22, 2017"
output: html_document
---
```{r}
# Takes a subsetted list of functions from Hadley Advanced R
# Assigns each randomly to a student in the class
# 19 February 2017
# NJG

# Ensure that the same random number sequence is used by everyone.
set.seed(100) 

# The Hadley R functions:
firstToLearn <- c("str", "?")

operators <- c("%in%", "match", "=", "<-", "<<-", "$", "[",
               "[[", "head", "tail", "subset", "with", "assign", "get")
comparisons <- c("all.equal", "identical", "!=", "==", ">", ">=", "<", "<=",  "is.na", "complete.cases",  "is.finite")

basicMath <- c("*", "+", "-", "/", "^", "%%", "%/%", "abs", "sign", "acos", "asin", "atan", "atan2", "sin", "cos", "tan", "ceiling", "floor", "round", "trunc", "signif", "exp", "log", "log10", "log2", "sqrt", "max", "min", "prod", "sum", "cummax", "cummin", "cumprod", "cumsum", "diff", "pmax", "pmin", "range", "mean", "median", "cor", "sd", "var", "rle")

logicalSets <- c("&", "|", "!", "xor", "all", "any", "intersect", "union", "setdiff", "setequal", "which")

vectorsMatrices <- c("c", "matrix", "length", "dim", "ncol", "nrow", "cbind", "rbind", "names", "colnames", "rownames", "t", "diag", "sweep", "as.matrix", "data.matrix")

makingVectors <- c("c", "rep", "rep_len", "seq", "seq_len", "seq_along", "rev", "sample", "choose", "factorial", "combn", "is.character", "is.numeric", "is.logical", "as.character", "as.numeric", "as.logical")

listsDataFrames <- c("list", "unlist",  "data.frame", "as.data.frame", "split", "expand.grid")

output <- c("print", "cat", "message", "warning", "dput", "format", "sink", "capture.output", "sprintf")

readingWritingData <- c("data", "count.fields", "read.csv", "write.csv", "read.delim", "write.delim", "read.fwf", "readLines", "writeLines", "readRDS", "saveRDS", "load", "save")

# Combine all of the function lists and randomize the order:
RFunctions <- c(firstToLearn, operators, comparisons, basicMath, logicalSets, vectorsMatrices, makingVectors, listsDataFrames, output, readingWritingData)

RFunctions <- sample(RFunctions)

# Create class list
classNames <- c("Alger", "Ashlock", "Burnham", "Clark", "Kazenal", "Keller", "Looi", "Makhukov", "Mickuki", "Nevins", "Southgate") 

# Assign functions
functionAssignments <- rep_len(classNames, length.out=length(RFunctions))

# Bind the two columns into a data frame
functionsFinal <- data.frame(functionAssignments,RFunctions)

splitDF<- split(functionsFinal, functionsFinal$functionAssignments)
splitDF$Ashlock

```
###`acos`   

####Lauren Ashlock

The acos function calculates the arc-cosine for a given argument, x. The arccosine is the inverse cosine function of x, when -1<x<1.

```{r}
#acos function

z<- c(.2,.3,.4,.5)
acos(z)

```

###`load`
####Lauren Ashlock

- The load funtion loads R objects that have already been saved in R. The arguments for this function are the file, envir, and verbose.    
- The input for the file argument is a connection or character string that gives the name of the file you want to reload.   
- The envir argument designates the environment where you want the data to be loaded. This can be useful for avoiding any overwriting of existing objects with the same name in the current environment. It is best to use envir= to load the object into a different environment.   
- The verbose argument designates whether or not you want item names to be printed as they load.This argument can be useful for debugging. The output of this function is a character vector of the names of objects created.   
- This is particularly useful for saving and reloading .Rdata or .Rhistory files (saving your workspace) into your current environment.

```{r}
#example
save.image(file= "homework_6.RData") #save your workspace

#To load this make sure you are in the current working directory
#in which you saved this workspace then run the following code

load(file= "homework_6.RData")

#the default settings are to load the file in the global environment and to have verbose = False. In order to debug...

load(file= "homework_6.Rdata",verbose= TRUE)
```


###`rbind`
####Lauren Ashlock

- rbind takes a sequence of vector, matrix, or data-frame areguments and combines them by rows.    
- Arguments: are vectors or matrices, that can be given as named arguments.   
- deparse.level is an integer argument that controls the construction of labels in the case of non-matrix-like arguments. The default is 0, which constructs no labels. 1 or 2 constructs labels from the argument names   
- make.row.names is an argument that is only used when binding data frames. It is a logical argument that indicates if unique and valid row.names should be constructed fromt the arguments.   
- stringsAsFactors is a logical argument that is passed to as.data.frame. This only has an effect when the arguments contain a non-data.frame) character   

```{r}
#example

m<- rbind(1,1:7)
m
m <- rbind(m, 8:14) 
m 

#deparse.level argument

dd<- 10
rbind(1:4, c=2, "a++"=10, deparse.level =0) #this names the rows of the middle two arguments

rbind(1:4, c=2, "a++"=10, dd, deparse.level=1) #this names the last three arguments (this is the default setting)

rbind(1:4, c=2, "a++" =10, dd, deparse.level=2) #takes the 










```


```{r}

```

