---
title: "Untitled"
output: html_document
---
### Have categorical x vars and continuous y vars, will run ANOVA on random data sets
### First run ANOVA on bare bones random data 


### ANOVA   
#### Summary Output

```{r}

aovSUM <- function(dataFrame=data){
     data <- cbind(as.factor(rep(c("Control","Toxic"),each=5)),c(rgamma(5,shape=5,scale=5),rgamma(5,shape=5,scale=10)))
     data
  x <- data[,1]
  y <- data[,2]
  aovMOD <- aov(y~x)
  myOUT <- summary(aovMOD)
  return(myOUT)
}

aovSUM()

##With dummy data

randomData <- (cbind(as.factor(rep(c("Maine","New Jersey"),each=5)),c(rgamma(8,shape=5,scale=5),rgamma(2,shape=5,scale=10))))

aovSUM(dataFrame = randomData)

```

### ANOVA
####Plot Output

```{r error=TRUE}

aovPLT <- function(dataFrame=data){
     data <- cbind(as.factor(rep(c("Control","Toxic"),each=5)),c(rgamma(5,shape=5,scale=5),rgamma(5,shape=5,scale=10)))
  x <- data[,1]
  y <- data[,2]
  aovMOD <- aov(y~x)
  boxplot(y~x,col=c("darkolivegreen1","darkgreen"), ylab="Fecundity")
}

aovPLT()

##With dummy data


randomData <- (cbind(as.factor(rep(c("Maine","New Jersey"),each=5)),c(rgamma(8,shape=5,scale=5),rgamma(2,shape=5,scale=10))))

aovPLT(dataFrame = randomData)
```
### Read in dataframe
#### Dummy data modeling expected results for cope selection experiment
#### These are my randomDataBling
##### These data were modeled looking at variables: Temp HAB and POP, two way interaction 
##### terms and three way interaction terms. Model assumed fecundity would be normally distributed, sd=15, variables explain 40% variation in fecundity, and a relationship factor of 0.5

```{r}
randomDataBling <- read.csv(file="copeDD", header=TRUE, sep=" ")
```




### ANOVA   
#### Summary Output

```{r}
##With randomDataBling

randomDataBling <- (cbind(as.factor(rep(c("Maine","New Jersey"),each=5)),c(rgamma(8,shape=5,scale=5),rgamma(2,shape=5,scale=10))))

aovSUM(dataFrame = randomDataBling)

```

### ANOVA
####Plot Output

```{r error=TRUE}

##With randomDataBling


randomDataBling <- (cbind(as.factor(rep(c("Maine","New Jersey"),each=5)),c(rgamma(8,shape=5,scale=5),rgamma(2,shape=5,scale=10))))

aovPLT(dataFrame = randomDataBling)

```
