---
title: "Untitled"
output: html_document
---
### Read in dataframe
### Dummy data modeling expected results for cope selection experiment

```{r}
dummyData <- read.csv(file="copeDD", header=TRUE, sep=" ")
```


##Modified Functions


### Linear Regression   
#### Summary Output
```{r}
linREGSUM <- function(dataFrame=data){
  data <- cbind(runif(10),runif(10))
  x <- data[,1]
  y <- data[,2]
  print(data)
  linMOD <- lm(y~x)
  myOUT <- summary(linMOD)
  return(myOUT)
}

linREGSUM()

##With dummy data

copepods <- cbind(runif(50),runif(50))

linREGSUM(dataFrame= copepods)

```

### Linear Regression   
#### Plot Output
```{r}
linREGPLT <- function(dataFrame=data){
   data <- cbind(runif(10),runif(10))
  x <- data[,1]
  y <- data[,2]
  linMOD <- lm(y~x)
  plot(y=y,x=x,pch=21,bg="lightblue",cex=2, main="Linear Regression", xlab="Generations of Exposure", ylab="Fecundity")
abline(linMOD, add=TRUE)
}

linREGPLT()

##With dummy data

copepods <- cbind(runif(50),runif(50))
linREGPLT(data = copepods)
```

### ANOVA   
#### Summary Output

```{r}

aovSUM <- function(dataFrame=data){
     data <- cbind(as.factor(rep(c("Control","Toxic"),each=5)),c(rgamma(5,shape=5,scale=5),rgamma(5,shape=5,scale=10)))
     data
  x <- data[,1]
  y <- data[,2]
  aovMOD <- aov(y~x)
  myOUT <- summary(aovMOD)
  return(myOUT)
}

aovSUM()

##With dummy data

copepods <- (cbind(as.factor(rep(c("Maine","New Jersey"),each=5)),c(rgamma(8,shape=5,scale=5),rgamma(2,shape=5,scale=10))))

aovSUM(dataFrame = copepods)

```

### ANOVA
####Plot Output

```{r}

aovPLT <- function(dataFrame=data){
     data <- cbind(as.factor(rep(c("Control","Toxic"),each=5)),c(rgamma(5,shape=5,scale=5),rgamma(5,shape=5,scale=10)))
  x <- data[,1]
  y <- data[,2]
  aovMOD <- aov(y~x)
  boxplot(y~x,col=c("darkolivegreen1","darkgreen"), ylab="Fecundity")
}

aovPLT()

##With dummy data

copepods <- (cbind(as.factor(rep(c("Maine","New Jersey"),each=5)),c(rgamma(8,shape=5,scale=5),rgamma(2,shape=5,scale=10))))

aovPLT(dataFrame = copepods)

```


###Contingency Table
####Summary Output

```{r}
ContingencySUM <- function(dataFrame= data){
  data <- rbind(c(90,98,89), c(70,60,20))
  x <- data[1,]
  y <- data[2,]
  rownames(dataFrame) <- c("Control","Toxic")
  colnames(dataFrame) <-c("LowTOX",
                         "MedTOX",
                         "HighTOX")
  myOUT <- print(chisq.test(dataFrame))
  return(myOUT)
}

ContingencySUM()

##With dummy data

copepods <- rbind(c(87,66, 77), c(66, 44, 23))

ContingencySUM(dataFrame = copepods)

```


###Contingency Table
#### Plot Output

```{r}
ContingencyPLT <- function(dataFrame= data){
  data <- rbind(c(90,98,89), c(70,60,20))
  x <- data[1,]
  y <- data[2,]
  rownames(dataFrame) <- c("Control","Toxic")
  colnames(dataFrame) <-c("LowTOX",
                         "MedTOX",
                         "HighTOX")
  barplot(height=dataFrame,
        beside=TRUE,
        col=c("darkolivegreen1","darkgreen"), ylim=c(0,max(colSums(dataFrame))), legend = rownames(dataFrame),args.legend=list(
      x=ncol(dataFrame) + 3,
      y=max(colSums(dataFrame)),
      bty = "n"
    ))
}

ContingencyPLT()

##With dummy data

copepods <- rbind(c(87,66, 77), c(66, 44, 23))

ContingencySUM(dataFrame = copepods)
```

###Logistic Regression
####Summary Output
```{r}

LogisticSUM <- function(dataFrame= data){
  data <- data.frame(xVar=rgamma(n=20,shape=5,scale=5),yVar=rbinom(n=20,size=1,p=0.5))
  logRegMod <- glm(yVar~xVar, data = data, family = binomial(link="logit"))
  summary(logRegMod)
}

LogisticSUM()

## With dummy data

copepods <- data.frame(xVar=rgamma(n=100,shape=7,scale=1),yVar=rbinom(n=100,size=1,p=0.2))

LogisticSUM(dataFrame=copepods)

```

###Logistic Regression
####Plot Output
```{r}
LogisticPLT <- function(dataFrame= data){
  data <- data.frame(xVar=rgamma(n=20,shape=5,scale=5),yVar=rbinom(n=20,size=1,p=0.5))
  logRegMod <- glm(yVar~xVar, data = data, family = binomial(link="logit"))
plot(x=dataFrame$xVar, y=dataFrame$yVar,pch=21,bg="gray31",cex=2, xlab = "Treatment Days", ylab = "Survival", main = "Toxic Algal Survival")
curve(predict(logRegMod,data.frame(xVar=x),type="response"),add=TRUE,lwd=2)
}

LogisticPLT()

## With dummy data

copepods <- data.frame(xVar=rgamma(n=100,shape=7,scale=1),yVar=rbinom(n=100,size=1,p=0.8))

LogisticPLT(dataFrame = copepods)

```

## Can run a few different ANOVAS with my dummyData

### ANOVA   
#### Summary Output

```{r}

aovSUM <- function(dataFrame=data){
     data <- cbind(as.factor(rep(c("Control","Toxic"),each=5)),c(rgamma(5,shape=5,scale=5),rgamma(5,shape=5,scale=10)))
     data
  x <- data[,1]
  y <- data[,2]
  aovMOD <- aov(y~x)
  myOUT <- summary(aovMOD)
  return(myOUT)
}

aovSUM()

##With dummy data

copepods <- (cbind(as.factor(rep(c("Maine","New Jersey"),each=5)),c(rgamma(8,shape=5,scale=5),rgamma(2,shape=5,scale=10))))

aovSUM(dataFrame = copepods)

```

### ANOVA
####Plot Output

```{r}

aovPLT <- function(dataFrame=data){
     data <- cbind(as.factor(rep(c("Control","Toxic"),each=5)),c(rgamma(5,shape=5,scale=5),rgamma(5,shape=5,scale=10)))
  x <- data[,1]
  y <- data[,2]
  aovMOD <- aov(y~x)
  boxplot(y~x,col=c("darkolivegreen1","darkgreen"), ylab="Fecundity")
}

aovPLT()

##With dummy data

copepods <- (cbind(as.factor(rep(c("Maine","New Jersey"),each=5)),c(rgamma(8,shape=5,scale=5),rgamma(2,shape=5,scale=10))))

aovPLT(dataFrame = copepods)

```