---
title: "Homework 5"
author: "Lauren Ashlock"
date: "February 15, 2017"
output: html_document
---

##Question 1
###Suppose x = 1.1, a = 2.2, and b = 3.3. Assign each expression to the value of the variable z and 
###print the value stored in z.

####Assigning values to x, a, and b
```{r}

x<- 1.1

a<- 2.2

b<- 3.3
```

####pt a
```{r}
z<- x^a^b
z
```

####pt b
```{r}
z<- (x^a)^b
z
```

####pt c
```{r}
z<- 3*x^3 + 2*x^2 + 1
z
```


####pt d
```{r}
floor((z%%1)*10)
```

####the z%%1 will grab everything after the 1s place (all decimals)   
####the floor(*10) grabs the digit in the first decimal place


##Question 2 Using the rep and seq functions create the following vectors

####pt a (1,2,3,4,5,6,7,8,7,6,5,4,3,2,1)

```{r}
SEQ1<- seq(1,8,1)
SEQ2<- seq(7,1,-1)
SEQ3<-c(SEQ1,SEQ2)
SEQ3
```


####pt b (1,2,2,3,3,3,4,4,4,4,5,5,5,5,5)
```{r}
c(1,rep(2,2),rep(3,3),rep(4,4),rep(5,5))
```



####pt c (5,4,4,3,3,3,2,2,2,2,1,1,1,1,1)
```{r}
c(5,rep(4,2),rep(3,3),rep(2,4),rep(1,5))
```


##Question 3
###Create a vector of two random uniform numbers. In a spatial map, these can be interpreted as x and y coordinates 
###that give the location of an individual (such as a marked forest tree in a plot that has been mapped). 
###Using one of R’s inverse trigonometry functions (asin(), acos(), or atan()), convert these numbers into 
###polar coordinates (If you don’t know what polar coordinates are, read about them on the web or in your calculus 
###textbook).
```{r}
xy<-c(runif(2))
xy

theta<-atan(xy[2]/xy[1])
theta

r<- sqrt((xy[2])^2+(xy[1])^2)
r

polarcoord<- c(r,theta)
polarcoord
```



##Question 4 
###Suppose that queue <- c("sheep", "fox", "owl", "ant") and that queue represents the animals 
###that are lined up to enter Noah’s Ark, with the sheep at the front of the line. Using R expressions, 
###update the queue successively as
```{r}
queue<- c("sheep","fox","owl","ant")
queue
```


####pt a the serpent arrives;
```{r}
append(queue,"serpent")
queue[5]<-"serpent"
```


####pt b the sheep enters the ark;
```{r}
queue<- queue[2:5]
queue
```


####pt c the donkey arrives and talks his way to the front of the line;
```{r}
queue<- c("donkey",queue)
queue
```


####pt d the serpent gets impatient and leaves;
```{r}
queue<-queue[1:4]
queue
```


####pt e the owl gets bored and leaves;
```{r}
queue<-queue[-3]
queue
```


####pt f the aphid arrives and the ant invites him to cut in line.
```{r}
queue<-c(queue[1:2],"aphid","ant")
queue
```


####pt g Finally, determine the position of the aphid in the line.
```{r}
which(queue=="aphid")
```


##Question 5 
###Use R to create a vector of all of the integers from 1 to 100 that are not divisible by 2, 3, or 7

```{r}

vec<- seq(1,100)
vec
vec2<- (vec %% 2!=0)&(vec %% 3!=0)&(vec %% 7!=0)

final<-vec[vec2]
final
```

##Question 6 
###Create a vector z of 1000 random uniform numbers
```{r}
z<- runif(1000)
head(z)
```


####pt a create a vector that contains 3 numbers: the proportion 
####of the numbers in z that are less than 0.10, greater than 0.90, and between 0.45 and 0.55.

```{r}
a<-which(z<0.1)

a<-length(a)
a
element1<-a/1000
element1

b<-which(z<0.9)

b<-length(b)
b
element2<-b/1000
element2

c<-which((z>.45)&(z<.55))
c<-length(c)
c

element3<-c/1000
element3


propvec<-c(element1,element2,element3)

propvec
```



####pt b Making successive copies of z, transform your vector of uniform numbers in the following ways:
####pt c for each case calculate your vector of 3 numbers to get the new proportions.
####log (base 10) of z
```{r}
z<-log(z)
head(z)

a<-which(z<0.1)

a<-length(a)
a
element1<-a/1000
element1

b<-which(z<0.9)

b<-length(b)
b
element2<-b/1000
element2

c<-which((z>.45)&(z<.55))
c<-length(c)
c

element3<-c/1000
element3


logzpropvec<-c(element1,element2,element3)

logzpropvec
```


####z^2
```{r}
z<- z^2
head(z)

a<-which(z<0.1)

a<-length(a)
a
element1<-a/1000
element1

b<-which(z<0.9)

b<-length(b)
b
element2<-b/1000
element2

c<-which((z>.45)&(z<.55))
c<-length(c)
c

element3<-c/1000
element3


zsquarepropvec<-c(element1,element2,element3)

zsquarepropvec
```


####e^z
```{r}
z<-exp(1)^z
head(z)


a<-which(z<0.1)

a<-length(a)
a
element1<-a/1000
element1

b<-which(z<0.9)

b<-length(b)
b
element2<-b/1000
element2

c<-which((z>.45)&(z<.55))
c<-length(c)
c

element3<-c/1000
element3


ezpropvec<-c(element1,element2,element3)

ezpropvec
```

####square root of z
```{r}
z<-sqrt(z)
head(z)

a<-which(z<0.1)

a<-length(a)
a
element1<-a/1000
element1

b<-which(z<0.9)

b<-length(b)
b
element2<-b/1000
element2

c<-which((z>.45)&(z<.55))
c<-length(c)
c

element3<-c/1000
element3


sqrtpropvec<-c(element1,element2,element3)

sqrtpropvec
```



